---
title: "F1 Fatal Events Analysis"
author: "Angela Lin"
date: "2025-12-01"
output:
  html_document:
    theme: default
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<style>

/* Custom styles for F1 Fatal Events Analysis */

/* F1 themed colors */
:root {
  --f1-red: #E10600;
  --f1-dark: #15151E;
}

/* Navbar styling */
.navbar {
  border-bottom: 3px solid var(--f1-red);
}

/* Code block styling */
.sourceCode {
  border-left: 3px solid var(--f1-red);
}

/* Card styling for callouts */
.callout {
  border-left-color: var(--f1-red);
}

/* Table styling */
table {
  margin-top: 1rem;
  margin-bottom: 1rem;
}

/* Footer styling */
.nav-footer {
  border-top: 3px solid var(--f1-red);
}

/* Iframe styling */
iframe {
  margin-top: 1rem;
}

</style>

# Introduction

This is your R Markdown document using the **custom F1-themed styling**.

You can add text, plots, and code chunks below.

---

# Example Code Chunk

```{r}
summary(cars)